### 2023-01-03 sections/experiments/real_world.qmd
online appendix done

## Real-World Data

include("src/setup.jl")
eval(setup)
output_path = output_dir("real_world")
www_path = www_dir("real_world")
```

@@

### Experiment

@@

img_files = readdir(www_path)[contains.(readdir(www_path),"line_chart")]
img_files = joinpath.(www_path,img_files)
for img in img_files
    display(load(img))
end
```

#### Error Bar Charts

@@

img_files = readdir(www_path)[contains.(readdir(www_path),"errorbar_chart")]
img_files = joinpath.(www_path,img_files)
for img in img_files
    display(load(img))
end
```

### Bootstrap

@@

@@

```{julia}
using DataFrames, Statistics
model_ = :FluxEnsemble
df = DataFrame() 
for (key, val) in results
    df_ = deepcopy(val.output)
    df_.dataset .= key
    df = vcat(df,df_)
end
df = df[df.n .== maximum(df.n),:]
df = df[df.model .== model_,:]
filter!(:value => x -> !any(f -> f(x), (ismissing, isnothing, isnan)), df)
gdf = groupby(df, [:generator, :dataset, :n, :name, :scope])
df_plot = combine(gdf, :value => (x -> [(mean(x),mean(x)+std(x),mean(x)-std(x))]) => [:mean, :ymax, :ymin])
df_plot = df_plot[[name in [:mmd, :model_performance] for name in df_plot.name],:]
df_plot = mapcols(x -> typeof(x) == Vector{Symbol} ? string.(x) : x, df_plot)
df_plot.name .= [r[:name] == "mmd" ? "$(r[:name])_$(r[:scope])" : r[:name] for r in eachrow(df_plot)]
transform!(df_plot, :dataset => (X -> [x=="cal_housing" ? "California Housing" : x for x in X]) => :dataset)
transform!(df_plot, :dataset => (X -> [x=="credit_default" ? "Credit Default" : x for x in X]) => :dataset)
transform!(df_plot, :dataset => (X -> [x=="gmsc" ? "GMSC" : x for x in X]) => :dataset)
transform!(df_plot, :name => (X -> [x=="mmd_domain" ? "MMD (domain)" : x for x in X]) => :name)
transform!(df_plot, :name => (X -> [x=="mmd_model" ? "MMD (model)" : x for x in X]) => :name)
transform!(df_plot, :name => (X -> [x=="model_performance" ? "Performance" : x for x in X]) => :name)
transform!(df_plot, :generator => (X -> [x=="REVISE" ? "Latent" : x for x in X]) => :generator)

@@

Images.load(joinpath(www_path,"paper_real_world_results.png"))
```

>>>>

# Real-World Data

```{julia}
#| echo: false
#| eval: true

include("src/setup.jl")
eval(setup)
output_path = output_dir("real_world")
www_path = www_dir("real_world")

# Artifacts:
# Images:
artifact_name = create_artifact_name_from_path(www_path, nothing)
_hash = artifact_hash(artifact_name, artifact_toml)
www_artifact_path = joinpath(artifact_path(_hash), artifact_name)
# Output:
artifact_name = create_artifact_name_from_path(output_path, nothing)
_hash = artifact_hash(artifact_name, artifact_toml)
output_artifact_path = joinpath(artifact_path(_hash), artifact_name)
```

@@

## Experiment

@@

img_files = readdir(www_artifact_path)[contains.(readdir(www_artifact_path),"line_chart")]
img_files = joinpath.(www_artifact_path,img_files)
for img in img_files
    display(load(img))
end
```

### Error Bar Charts

@@

img_files = readdir(www_artifact_path)[contains.(readdir(www_artifact_path),"errorbar_chart")]
img_files = joinpath.(www_artifact_path,img_files)
for img in img_files
    display(load(img))
end
```

## Bootstrap

@@

```{julia}
#| output: true
#| eval: true
#| echo: false

_file = readdir(output_artifact_path)[contains.(readdir(output_artifact_path),"bootstrap")]
_file = joinpath.(output_artifact_path, _file)
df = CSV.File(_file) |> DataFrame
df = df[.!(ismissing.(df.p_value)),:]
df = combine(groupby(df, [:name, :scope, :data, :model, :generator]), :p_value => mean)
ENV["LINES"] = size(df, 1)
pretty_table(df)
```

@@

using DataFrames, Statistics
model_ = :FluxEnsemble
df = DataFrame() 
for (key, val) in results
    df_ = deepcopy(val.output)
    df_.dataset .= key
    df = vcat(df,df_)
end
df = df[df.n .== maximum(df.n),:]
df = df[df.model .== model_,:]
filter!(:value => x -> !any(f -> f(x), (ismissing, isnothing, isnan)), df)
gdf = groupby(df, [:generator, :dataset, :n, :name, :scope])
df_plot = combine(gdf, :value => (x -> [(mean(x),mean(x)+std(x),mean(x)-std(x))]) => [:mean, :ymax, :ymin])
df_plot = df_plot[[name in [:mmd, :model_performance] for name in df_plot.name],:]
df_plot = mapcols(x -> typeof(x) == Vector{Symbol} ? string.(x) : x, df_plot)
df_plot.name .= [r[:name] == "mmd" ? "$(r[:name])_$(r[:scope])" : r[:name] for r in eachrow(df_plot)]
transform!(df_plot, :dataset => (X -> [x=="cal_housing" ? "California Housing" : x for x in X]) => :dataset)
transform!(df_plot, :dataset => (X -> [x=="credit_default" ? "Credit Default" : x for x in X]) => :dataset)
transform!(df_plot, :dataset => (X -> [x=="gmsc" ? "GMSC" : x for x in X]) => :dataset)
transform!(df_plot, :name => (X -> [x=="mmd_domain" ? "MMD (domain)" : x for x in X]) => :name)
transform!(df_plot, :name => (X -> [x=="mmd_model" ? "MMD (model)" : x for x in X]) => :name)
transform!(df_plot, :name => (X -> [x=="model_performance" ? "Performance" : x for x in X]) => :name)
transform!(df_plot, :generator => (X -> [x=="REVISE" ? "Latent" : x for x in X]) => :generator)

@@

Images.load(joinpath(www_artifact_path,"paper_real_world_results.png"))
```

### 2023-01-03 sections/experiments/synthetic.qmd
online appendix done

include("src/setup.jl")
eval(setup)
output_path = output_dir("synthetic") # output directory for artifacts
www_path = www_dir("synthetic")       # output directory for images
data_path = data_dir("synthetic")
```

@@

```{julia}
#| output: true
#| fig-cap: "Line Charts"
#| fig-subcap: 
#|      - "Circles"
#|      - "Linearly Separable"
#|      - "Moons"
#|      - "Overlapping"
#| layout-ncol: 1
#| label: fig-line
#| eval: true

img_files = readdir(www_path)[contains.(readdir(www_path),"line_chart")]
img_files = joinpath.(www_path,img_files)
for img in img_files
    display(Images.load(img))
end
```

@@

```{julia}
#| output: true
#| fig-cap: "Error Bar Charts"
#| fig-subcap: 
#|      - "Circles"
#|      - "Linearly Separable"
#|      - "Moons"
#|      - "Overlapping"
#| layout-ncol: 1
#| label: fig-error
#| eval: true

img_files = readdir(www_path)[contains.(readdir(www_path),"errorbar_chart")]
img_files = joinpath.(www_path,img_files)
for img in img_files
    display(Images.load(img))
end
```

@@

```{julia}
using DataFrames, Statistics
df = results[:overlapping].output
df = df[[x ∈ maximum(df.n) for x in df.n],:]
gdf = groupby(df, [:generator, :model, :n, :name, :scope])
df_plot = combine(gdf, :value => (x -> [(mean(x),mean(x)+std(x),mean(x)-std(x))]) => [:mean, :ymax, :ymin])
df_plot = df_plot[[name in [:decisiveness, :disagreement, :mmd, :mmd_grid, :model_performance] for name in df_plot.name],:]
df_plot = df_plot[.!(df_plot.name.==:mmd .&& df_plot.scope.==:model),:]
df_plot = mapcols(x -> typeof(x) == Vector{Symbol} ? string.(x) : x, df_plot)
transform!(df_plot, :name => (X -> [x=="decisiveness" ? "Decisiveness" : x for x in X]) => :name)
transform!(df_plot, :name => (X -> [x=="disagreement" ? "Disagreement" : x for x in X]) => :name)
transform!(df_plot, :name => (X -> [x=="mmd" ? "MMD (domain)" : x for x in X]) => :name)
transform!(df_plot, :name => (X -> [x=="mmd_grid" ? "MMD (model)" : x for x in X]) => :name)
transform!(df_plot, :name => (X -> [x=="model_performance" ? "Performance" : x for x in X]) => :name)
transform!(df_plot, :generator => (X -> [x=="REVISE" ? "Latent" : x for x in X]) => :generator)
transform!(df_plot, :model => (X -> [x=="FluxEnsemble" ? "Deep Ensemble" : x for x in X]) => :model)
transform!(df_plot, :model => (X -> [x=="FluxModel" ? "MLP" : x for x in X]) => :model)
transform!(df_plot, :model => (X -> [x=="LogisticRegression" ? "Linear" : x for x in X]) => :model)

@@

Images.load(joinpath(www_path,"paper_synthetic_results.png"))
```

>>>>

include("src/setup.jl")
eval(setup)
output_path = output_dir("synthetic") # output directory for artifacts
www_path = www_dir("synthetic")       # output directory for images
data_path = data_dir("synthetic")

# Artifacts:
# Images:
artifact_name = create_artifact_name_from_path(www_path, nothing)
_hash = artifact_hash(artifact_name, artifact_toml)
www_artifact_path = joinpath(artifact_path(_hash), artifact_name)
# Output:
artifact_name = create_artifact_name_from_path(output_path, nothing)
_hash = artifact_hash(artifact_name, artifact_toml)
output_artifact_path = joinpath(artifact_path(_hash), artifact_name)
```

@@

```{julia}
#| output: true
#| fig-cap: "Line Charts"
#| fig-subcap: 
#|      - "Circles"
#|      - "Linearly Separable"
#|      - "Moons"
#|      - "Overlapping"
#| layout-ncol: 1
#| label: fig-line
#| eval: true
#| echo: false

img_files = readdir(www_artifact_path)[contains.(readdir(www_artifact_path),"line_chart")]
img_files = joinpath.(www_artifact_path,img_files)
for img in img_files
    display(Images.load(img))
end
```

@@

```{julia}
#| output: true
#| fig-cap: "Error Bar Charts"
#| fig-subcap: 
#|      - "Circles"
#|      - "Linearly Separable"
#|      - "Moons"
#|      - "Overlapping"
#| layout-ncol: 1
#| label: fig-error
#| eval: true
#| echo: false

img_files = readdir(www_artifact_path)[contains.(readdir(www_artifact_path),"errorbar_chart")]
img_files = joinpath.(www_artifact_path,img_files)
for img in img_files
    display(Images.load(img))
end
```

@@

```{julia}
#| echo: false

using DataFrames, Statistics
df = results[:overlapping].output
df = df[[x ∈ maximum(df.n) for x in df.n],:]
gdf = groupby(df, [:generator, :model, :n, :name, :scope])
df_plot = combine(gdf, :value => (x -> [(mean(x),mean(x)+std(x),mean(x)-std(x))]) => [:mean, :ymax, :ymin])
df_plot = df_plot[[name in [:decisiveness, :disagreement, :mmd, :mmd_grid, :model_performance] for name in df_plot.name],:]
df_plot = df_plot[.!(df_plot.name.==:mmd .&& df_plot.scope.==:model),:]
df_plot = mapcols(x -> typeof(x) == Vector{Symbol} ? string.(x) : x, df_plot)
transform!(df_plot, :name => (X -> [x=="decisiveness" ? "Decisiveness" : x for x in X]) => :name)
transform!(df_plot, :name => (X -> [x=="disagreement" ? "Disagreement" : x for x in X]) => :name)
transform!(df_plot, :name => (X -> [x=="mmd" ? "MMD (domain)" : x for x in X]) => :name)
transform!(df_plot, :name => (X -> [x=="mmd_grid" ? "MMD (model)" : x for x in X]) => :name)
transform!(df_plot, :name => (X -> [x=="model_performance" ? "Performance" : x for x in X]) => :name)
transform!(df_plot, :generator => (X -> [x=="REVISE" ? "Latent" : x for x in X]) => :generator)
transform!(df_plot, :model => (X -> [x=="FluxEnsemble" ? "Deep Ensemble" : x for x in X]) => :model)
transform!(df_plot, :model => (X -> [x=="FluxModel" ? "MLP" : x for x in X]) => :model)
transform!(df_plot, :model => (X -> [x=="LogisticRegression" ? "Linear" : x for x in X]) => :model)

@@

Images.load(joinpath(www_artifact_path,"paper_synthetic_results.png"))
```
